Workflow Part II: Inverse root modeling and post-processing

### 2021-02-20 Readme.Rmd
Cleaned

Script to load data generated from the data preparation script above for use in inverse model as well as manuscript

```{r Chunk 06.0, eval = FALSE}
source("code/06.0_load.R")
```

@@

```{r Chunk 08.0, eval = FALSE}
source("code/08.0_manuscript_data_figs.R")
```

@@

```{r Chunk 09.0, eval = FALSE}
source("code/09.0_manuscript.rmd")
```

@@

```{r Chunk 10.0, eval = FALSE}
source("code/10.0_Supporting_Information.Rmd")
```

>>>>

Script to load data generated from the data preparation script above for use in inverse model as well as manuscript. It's needed for rest of the scripts.

<!-- ```{r Chunk 06.0, eval = FALSE} -->
<!-- source("code/06.0_load.R") -->
<!-- ``` -->

@@

```{r Chunk 08.0, eval = FALSE}
source("code/06.0_load.R")
source("code/08.0_manuscript_data_figs.R")
```

@@

```{r Chunk 09.0, eval = FALSE}
render("09.0_manuscript.rmd", output_format = "bookdown::html_document2")
```

@@

```{r Chunk 10.0, eval = FALSE}
render("10.0_Supporting_Information.Rmd", output_format = "bookdown::html_document2")
```
